Web-based Supplementary Materials for A Space-time \Skewt Model for Threshold Exceedances by Morris, Reich, Thibaud, and Cooley

### 2016-06-29 LaTeX/supplemental_rev.tex
updates to manuscript for revision

\section{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{sta:proofsamepartition}
Let $c$ be the midpoint of $\bs_1$ and $\bs_2$.
Define $A$ as the circle centered at $c$ with radius $h / 2$ where $h = ||\bs_1 - \bs_2||$ is the distance between sites $\bs_1$ and $\bs_2$.
Consider a homogeneous spatial Poisson process over $A$ with intensity given by
\begin{align*}
  \mu_{PP}(A) = \lambda_{PP} |A| = \lambda_{PP} \pi \left(\frac{h}{2}\right)^2 = \lambda_{PPA}^* h^2.
\end{align*}
Consider a partition of $A$ into four regions, $B_1$, $B_2$, $R_1$, $R_2$ as seen in \fref{stfig:hpp}.
\begin{figure}
  \includegraphics[width=\linewidth]{plots/circles}
  \caption{Illustration of the partition of $A$.}
  \label{stfig:hpp}
\end{figure}
Let $N_i$ be the number of knots in $B_i$ and $L_i = l$ if $\bs_i \in P_l$ for $i = 1, 2$.
Then
\begin{align}
  P(L_1 \neq L_2) \ge P(N_1 > 0, N_2 > 0)
\end{align}
since knots in both $B_1$ and $B_2$ is sufficient, but not necessary, to ensure that $\bs_1$ and $\bs_2$ are in different partition sets.
By definition of a Poission process, $N_1$ and $N_2$ are independent and thus $P(N_1 > 0, N_2 > 0) = P(N_1 > 0)^2$, and the intensity measure over $B_1$ is given by
\begin{align}
  \mu_{PP}(B_1) &= \lambda_{PP} |B_1| = \lambda_{PP} \frac{h^2}{4} \left(\frac{2 \pi}{3} - \frac{\sqrt{3}}{2} \right) \nonumber \\
       &= \lambda^*_{PPB1} h^2.
\end{align}
So,
\begin{align}
  P(L_1 \neq L_2) >= P(N_1 > 0)^2 = [1 - P(N_1 = 0)]^2 = [1 - \exp\left(-\lambda^*_{PPB1} h^2\right)]^2
\end{align}
which goes to 1 as $h$ goes to infinity.

@@

\section{Comparisons with other parameterizations} \label{sta:otherparams}
Various forms of multivariate skew-normal and \skewt distributions have been proposed in the literature.
In this section, we make a connection between our parameterization in \eref{steq:fullmodel} of the main text and another popular version.
\citet{Azzalini2014} and \citet{Beranger2016} define a skew-normal process as
\begin{align}
  \tilde{X}(\bs) = \tilde{\lambda}|z| + (1 - \tilde{\lambda}^2)^{1 / 2} v(\bs)
\end{align}
where $\tilde{\lambda} \in (-1, 1)$, $z \sim N(0, 1)$, and $v(\bs)$ is a Gaussian process with mean zero, variance one, and spatial correlation function $\rho$.
To extend this to the \skewt distribution, \citet{Azzalini2003} take $\tilde{Y}(\bs) = W\tilde{X}(\bs)$ where $W^{-2} \sim $ Gamma$(a / 2, a / 2)$.
Returning to the proposed parameterization (with $\bbeta = 0$), let $W^{-2} = \frac{b}{a}\sigma^{-2} \sim$ Gamma$(a / 2, a / 2)$ so that \eref{steq:fullmodel} in the manuscript becomes
\begin{align}
  Y(\bs) = W \left[ \lambda \left(\frac{b}{a}\right)^{1 / 2} |z| + \left(\frac{b}{a}\right)^{1 / 2} v(\bs) \right].
\end{align}
Clearly setting $b = a (1 - \tilde{\lambda}^2) > 0$, and $\lambda = \tilde{\lambda} / (1 - \tilde{\lambda}^2)^{1 / 2} \in (-\infty, \infty)$ resolves the difference in parameterizations.
We note that our parameterization has three parameters $(a, b, \lambda)$ compared to the two parameters of the alternative parameterization $(a, \tilde{\lambda})$.
Since we have assumed that both $v(\bs)$ and $z$ have unit scale, the additional $b$ parameter in our parameterization is required to control the precision.
% However, if we introduce an overall scale parameter $c > 0$ into the alternative parameterization so that $\tilde{Y}(\bs) = c W \tilde{X}(\bs)$, then the two models remain equivalent by setting $a = \nu$, $b = \frac{\nu}{c^2 (1 - \tilde{\lambda}^2)}$, and $\lambda = \tilde{\lambda} / (1 - \tilde{\lambda}^2)^{1 / 2}$.

@@

\section{Brier scores for ozone prediction} \label{sta:ozonesite}
Because typical ozone concentration varies throughout the US, we have included Brier scores by site for two model fits (Gaussian and \Skewt, $K = 5$, $T = 50$) in \fref{stfig:bssite}.
As we can see in these plots, both models seem to perform similarly across the US with the poorest performance in California.
Other methods have similar Brier score maps to these.
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{plots/bs-site}
  \caption{Map of Brier scores for Gaussian (top) vs \Skewt, $K = 5$, $T = 50$ (bottom).}
  \label{stfig:bssite}
\end{figure}

@@

\begin{table}[htbp]
  \centering
  \caption{Setting 4 -- Max-stable}
  \label{sttbl:mssim}
  \begin{tabular}{|l|cccc|cccc|ccc|ccc|}
    \cline{2-15}
    \multicolumn{1}{c}{} & \multicolumn{4}{|c}{$q(0.90)$} & \multicolumn{4}{|c}{$q(0.95)$} & \multicolumn{3}{|c}{$q(0.98)$} & \multicolumn{3}{|c|}{$q(0.99)$} \\
    \hline
    Method 1 & A & B &   &   &   & B &   &   &   & B &   &   &   & C \\
    \hline
    Method 2 &   & B &   &   &   & B &   &   &   & B &   &   & B & C \\
    \hline
    Method 3 &   &   & C & D &   &   & C &   &   & B &   &   & B &   \\
    \hline
    Method 4 &   &   &   & D &   &   &   & D &   &   & C &   &   & C \\
    \hline
    Method 5 &   &   & C &   &   & B & C &   &   & B &   &   & B & C \\
    \hline
    Method 6 & A &   &   &   & A &   &   &   & A &   &   & A &   &   \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{Setting 5 -- Brown Resnick}
  \label{sttbl:transsim}
  \begin{tabular}{|l|cccc|ccc|ccc|ccc|}
    \cline{2-14}
    \multicolumn{1}{c}{} & \multicolumn{4}{|c}{$q(0.90)$} & \multicolumn{3}{|c}{$q(0.95)$} & \multicolumn{3}{|c}{$q(0.98)$} & \multicolumn{3}{|c|}{$q(0.99)$} \\
    \hline
    Method 1 &   &   &   & D &   &   & C &   &   & C &   &   & C \\
    \hline
    Method 2 &   &   &   & D &   &   & C &   &   & C &   &   & C \\
    \hline
    Method 3 & A & B &   &   & A &   &   & A & B &   &   & B &   \\
    \hline
    Method 4 &   &   & C &   &   & B &   &   & B &   &   & B &   \\
    \hline
    Method 5 & A &   &   &   & A &   &   & A &   &   & A & B &   \\
    \hline
    Method 6 &   & B & C &   & A &   &   & A &   &   & A &   &   \\
    \hline
  \end{tabular}
\end{table}

>>>>

\section{Proof that $\lim_{h \rightarrow \infty} \pi(h) = 0$} \label{sta:proofsamepartition}
Let $c$ be the midpoint of $\bs_1$ and $\bs_2$.
Define $A$ as the circle centered at $c$ with radius $h / 2$ where $h = ||\bs_1 - \bs_2||$ is the distance between sites $\bs_1$ and $\bs_2$.
Consider a homogeneous spatial Poisson process over $A$ with intensity $\lambda_{PP}$, so that
\begin{align*}
  \mu_{PP}(A) = \lambda_{PP} |A| = \lambda_{PP} \pi \left(\frac{h}{2}\right)^2 = \lambda_{PPA}^* h^2.
\end{align*}
Consider a partition of $A$ into four regions, $B_1$, $B_2$, $R_1$, $R_2$ as seen in \fref{stfig:hpp}.
\begin{figure}
  \includegraphics[width=\linewidth]{plots/circles}
  \caption{Illustration of the partition of $A$.}
  \label{stfig:hpp}
\end{figure}
Let $N_i$ be the number of knots in $B_i$ and $L_i = l$ if $\bs_i \in P_l$ for $i = 1, 2$.
Then
\begin{align}
  P(L_1 \neq L_2) \ge P(N_1 > 0, N_2 > 0)
\end{align}
since knots in both $B_1$ and $B_2$ is sufficient, but not necessary, to ensure that $\bs_1$ and $\bs_2$ are in different partition sets.
By definition of a Poission process, $N_1$ and $N_2$ are independent and thus $P(N_1 > 0, N_2 > 0) = P(N_1 > 0)^2$, and
\begin{align}
  \mu_{PP}(B_1) &= \lambda_{PP} |B_1| = \lambda_{PP} \frac{h^2}{4} \left(\frac{2 \pi}{3} - \frac{\sqrt{3}}{2} \right) \nonumber \\
       &= \lambda^*_{PPB1} h^2.
\end{align}
So,
\begin{align}
  P(L_1 \neq L_2) >= P(N_1 > 0)^2 = [1 - P(N_1 = 0)]^2 = [1 - \exp\left(-\lambda^*_{PPB1} h^2\right)]^2
\end{align}
which goes to 1 as $h$ goes to infinity.

@@

\section{Comparisons with other parameterizations} \label{sta:otherparams}
Various forms of multivariate skew-normal and \skewt distributions have been proposed in the literature.
In this section, we make a connection between our parameterization in \eref{steq:fullmodel} of the main text and another popular version.
\citet{Azzalini2014} and \citet{Beranger2016} define a skew-normal process as
\begin{align}
  \tilde{X}(\bs) = \tilde{\lambda}|z| + (1 - \tilde{\lambda}^2)^{1 / 2} v(\bs)
\end{align}
where $\tilde{\lambda} \in (-1, 1)$, $z \sim N(0, 1)$, and $v(\bs)$ is a Gaussian process with mean zero, variance one, and spatial correlation function $\rho$.
To extend this to the \skewt distribution, \citet{Azzalini2003} take $\tilde{Y}(\bs) = W\tilde{X}(\bs)$ where $W^{-2} \sim $ Gamma$(a / 2, a / 2)$.
Returning to the proposed parameterization (with $\bbeta = 0$), let $W^{-2} = \frac{b}{a}\sigma^{-2}$ so that \eref{steq:fullmodel} in the manuscript becomes
\begin{align}
  Y(\bs) = W \left[ \lambda \left(\frac{b}{a}\right)^{1 / 2} |z| + \left(\frac{b}{a}\right)^{1 / 2} v(\bs) \right].
\end{align}
Clearly setting $b / a = (1 - \tilde{\lambda}^2) > 0$, and $\lambda = \tilde{\lambda} / (1 - \tilde{\lambda}^2)^{1 / 2} \in (-\infty, \infty)$ resolves the difference in parameterizations.
We note that our parameterization has three parameters $(a, b, \lambda)$ compared to the two parameters of the alternative parameterization $(a, \tilde{\lambda})$.
Since we have assumed that both $v(\bs)$ and $z$ have unit scale, the additional $b$ parameter in our parameterization is required to control the precision.
% However, if we introduce an overall scale parameter $c > 0$ into the alternative parameterization so that $\tilde{Y}(\bs) = c W \tilde{X}(\bs)$, then the two models remain equivalent by setting $a = \nu$, $b = \frac{\nu}{c^2 (1 - \tilde{\lambda}^2)}$, and $\lambda = \tilde{\lambda} / (1 - \tilde{\lambda}^2)^{1 / 2}$.

@@

\section{Brier scores for ozone prediction} \label{sta:ozonesite}
Because typical ozone concentration varies throughout the US, we have included Brier scores for exceedance of the 99th quantile by site for two model fits (Gaussian and Symmetric-$t$, $K = $ 10 knots, $T = $ 75, time series) in \fref{stfig:bssite}.
As we can see in these plots, both models seem to perform similarly across the US with the poorest performance in California.
Other methods have similar Brier score maps to these.
\begin{figure}
  \centering
  \includegraphics[width=0.8\linewidth]{plots/bs-site}
  \caption{Map of Brier scores for Gaussian (top) vs Symmetric-$t$, $K = $ 10 knots, $T = $ 75, time series (bottom).}
  \label{stfig:bssite}
\end{figure}

@@

\begin{table}[htbp]
  \centering
  \caption{Setting 4 -- Max-stable, Asymmetric logistic}
  \label{sttbl:mssim}
  \begin{tabular}{|l|cccc|cccc|ccc|ccc|}
    \cline{2-15}
    \multicolumn{1}{c}{} & \multicolumn{4}{|c}{$q(0.90)$} & \multicolumn{4}{|c}{$q(0.95)$} & \multicolumn{3}{|c}{$q(0.98)$} & \multicolumn{3}{|c|}{$q(0.99)$} \\
    \hline
    Method 1 & A & B &   &   &   & B &   &   &   & B &   &   &   & C \\
    \hline
    Method 2 &   & B &   &   &   & B &   &   &   & B &   &   & B & C \\
    \hline
    Method 3 &   &   & C & D &   &   & C &   &   & B &   &   & B &   \\
    \hline
    Method 4 &   &   &   & D &   &   &   & D &   &   & C &   &   & C \\
    \hline
    Method 5 &   &   & C &   &   & B & C &   &   & B &   &   & B & C \\
    \hline
    Method 6 & A &   &   &   & A &   &   &   & A &   &   & A &   &   \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[htbp]
  \centering
  \caption{Setting 5 -- Max-stable, Brown-Resnick}
  \label{sttbl:transsim}
  \begin{tabular}{|l|cccc|ccc|ccc|ccc|}
    \cline{2-14}
    \multicolumn{1}{c}{} & \multicolumn{4}{|c}{$q(0.90)$} & \multicolumn{3}{|c}{$q(0.95)$} & \multicolumn{3}{|c}{$q(0.98)$} & \multicolumn{3}{|c|}{$q(0.99)$} \\
    \hline
    Method 1 &   &   &   & D &   &   & C &   &   & C &   &   & C \\
    \hline
    Method 2 &   &   &   & D &   &   & C &   &   & C &   &   & C \\
    \hline
    Method 3 & A & B &   &   & A &   &   & A & B &   &   & B &   \\
    \hline
    Method 4 &   &   & C &   &   & B &   &   & B &   &   & B &   \\
    \hline
    Method 5 & A &   &   &   & A &   &   & A &   &   & A & B &   \\
    \hline
    Method 6 &   & B & C &   & A &   &   & A &   &   & A &   &   \\
    \hline
  \end{tabular}
\end{table}
